```{r}
#| include: false
library("tidyverse")
library("sf")
library("plotly")
library("purrr")
library("paletteer")
```

This folder contains the code I have used to generate maps that have the different hospitals etc in it. 

\

My own purpose is to visualize where the labtests are performed and requisitioned. However, it might be of use to other people as well. 

\

The readme was written in Quarto, but converted into md for the sake of github. Pre-plotting steps are perfomed in python, plotting in R.

\

Important resources are: 

1. Medcom - Information on all medical providers
   1. Henvisningstabel: https://medcom.dk/projekter/pakkehenvisninger/henvisningstabellen/
      1. Information on the service provided (but has some ydernumre)
2. SHAK-codes - Sygehus-afdelingsklassifikation
   1. https://sor-filer.sundhedsdata.dk/sor_produktion/data/shak/
3. SOR-codes - sundhedsvæsnets organisationsregister
   1. https://sor-filer.sundhedsdata.dk/sor_produktion/data/sor/
4. DAWA - geographical information based on addresses 
   1. Used via API to find coordinate / municipality of a given address

## Files:

All files are saved as geojson - very like json but with a geometry column that contains coordinates that can be plotted. Geopandas also have a lot of tools for working with the geometries.

## Scripts: 

3 main scripts are there: 

1. data.py 
   1. Contains the data loading. Loads from the above mentioned webpages. 
2. coordinates.py
   1. Adapts the loaded data and makes geojson files that contain stuff for plotting. 
3. plotting.r
   1. Code for plotting the geojson in r. This includes code for loading the geojson and converting it to a tibble. This can also be done in python - although the geojsons can be directly loaded and plotted in geopandas / matplotlib. 

## Plot examples: 

Some examples of: 

1. Denmark and administrative divisions. 
2. Different Healthcare institutions. 

```{r}
#| include: false
#|

# Data Denmark
denmark_g <- sf::st_read("data/denmark.geojson")
denmark_coord <- as_tibble(st_coordinates(denmark_g)) |>
    group_by(L1, L2, L3) |>
    mutate(
        order = row_number(),
        group_id = cur_group_id()
    ) |>
    ungroup()

# now the
regions_g <- sf::st_read("/home/jenswaaben/phd/software/adress_mapping/data/regions.geojson") |>
    st_collection_extract(type = c("POLYGON")) |>
    st_cast("MULTIPOLYGON")
region_names <- regions_g |>
    st_drop_geometry() |>
    as_tibble() |>
    mutate(L3 = row_number()) |>
    select(L3, navn)
regions_coord <- as_tibble(st_coordinates(regions_g)) |>
    left_join(region_names) |>
    group_by(L1, L2, L3) |>
    mutate(
        order = row_number(),
        group_id = cur_group_id()
    ) |>
    ungroup()

```

### Plots of Denmark: 

First of a simple plot of Denmark. The colors are just individual "blobs". 

```{r}
#| echo: false

denmark_coord |>
    ggplot(mapping = aes(x = X, y = Y, group = group_id)) +
    geom_polygon(fill = "blue") +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.background = element_rect(color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank()
    ) +
    scale_fill_paletteer_c("ggthemes::Orange-Blue Diverging")


```

Then the regions: 

```{r}
#| echo: false

ggplot(data = regions_coord) +
    geom_polygon(mapping = aes(x = X, y = Y, group = group_id, fill = navn)) +
    theme_minimal() +
    theme(
        legend.position = "none",
        panel.background = element_rect(color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text = element_blank(),
        axis.title = element_blank()
    ) +
    scale_fill_paletteer_d("tvthemes::WaterTribe")

```
